Consistency scores in text data

### 2020-07-14 outputs/documents/paper.Rmd
Add plan for appendix
introduction GPT-3 part revision

The model that we use to forecast is GPT-3 by OpenAI. OpenAI is... **(Ke-Li to add a two sentence summary in boring academic language)**. GPT-3 is... **(Ke-Li to add a three sentence summary in boring academic language)**.

@@

>>>>

The model that we use to forecast is GPT-3 by OpenAI. OpenAI is an artificial intelligent research group who claims to be an pursuer of beneficial artificial general intelligence. Their works, including GPT-3, have a focus on generative models who have the capacity to generate data tha resemble human creation. GPT-3, the Generative Pretrained Transformer 3, is an unsupervised language model that has more than 175 billions of parameters, referring to the weights of the connections that enable the neural network to learn **(Keli add citation)**. GPT-3 can learn NLP tasks with few examples and without task-specific dataset **(Keli add citation)**. This means GPT-3 can learns like human do, which makes the creation of NLP technologies more accessible.

@@

## Discussion of how GPT-3 works

**(Ke-Li - it would be good for us to go through how it actually works in as much detail as we can manage (in our own words). This is mostly just to force us to learn how it works and may be taken out of the final version of the paper, but it's still an important exercise.)**
